Reinforcement-Learning Windturbine Controller

### 2019-11-14 paper/paper.tex
Added twin delayed features

We observed that our Q-Loss, especially after a death, explodes into e15 magnitude values, while most of the times it stayed around e2 magnitude. Instable Q-Losses are a general problem with DQN and DDPG, and some literature \cite{fujimotoAddressingFunctionApproximation2018} proposes to use two Q networks, of which only the minimum is used for training. We could already greatly improve our results by using huber-loss \cite{huber1964} for the critic instead of mean squared error loss as described in DDPG paper. Also, we believe that adding double Q networks such as in \cite{fujimotoAddressingFunctionApproximation2018} would also solve this problem.

@@

% What should I put here?

>>>>

We observed that our Q-Loss, especially after a death, explodes into e15 magnitude values, while most of the times it stayed around e2 magnitude. Instable Q-Losses are a general problem with DQN and DDPG, and some literature \cite{fujimotoAddressingFunctionApproximation2018} proposes to use two Q networks, of which only the minimum is used for training.

\subsection{Huber loss}
We could already greatly improve our results by using huber-loss \cite{huber1964} for the critic instead of mean squared error loss as described in DDPG paper. However we still saw some loss explosions.

\subsection{Double critic}
Adding twin critic networks such as in \cite{fujimotoAddressingFunctionApproximation2018} eventually solved our problem with loss explosions completely.

@@

We name our final variant of \ac{DDPG} \ac{DDDDDPPG}. Our variant is different to \cite{fujimotoAddressingFunctionApproximation2018} in that we don't use target policy smoothing. However, we just have more D.
% What should I put here?
